\documentclass[]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript

\usepackage{fullpage}
\usepackage[top=.4in, bottom=0in, left=.7in, right=1in]{geometry}

% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\author{}
\date{}

\begin{document}

\section{Vansh Khanna}

404 East Stoughton Street, Champaign, IL • (217)281-2507 •
vkhanna2@illinois.edu • vanshk.com • github.com/VanshKhanna •
linkedin.com/in/KhannaVansh

\subsection{Education}

\begin{itemize}
\item
  \textbf{B.S in Computer Engineering at University of Illinois at
  Urbana Champaign}, \emph{2012-2016}\\ \textbf{GPA}: 3.60/4.00\\
  \textbf{Honors}: Dean's List • James Scholar\\
  \textbf{Extra-Curricular}: Member of Eta Kappa Nu (IEEE Honor Society)
  • Editor for IEEE SPARK@UIUC\\ \textbf{Coursework}: Computer Systems
  Engineering (ECE 391), Digital Signal Processing, Communication
  Networks, Algorithms and Models of Computation, {[}\emph{Distributed
  Systems, Wireless Networks, Practical Machine Learning}{]}
\end{itemize}

\subsection{Experience}

\begin{itemize}
\item
  \textbf{Intern at Akuna Capital (Champaign, Illinois)}, \emph{Summer
  2014}

  System side development for a Market Interface System. System was used
  traders to test strategies for one of firm's most heavily traded
  exchanges. Implemented the Order Entry Side of the exchange. Wrote
  unit tests for the order entry side. Developed a series of tests to
  check integrated functionality with the incoming Market Data.
\item
  \textbf{Intern at NIIT Technologies, Ltd (Noida, India)}, \emph{Summer
  2013}

  Wrote a time efficient algorithm in C++ to parse and edit captured
  TCP/IP packets. Used AVL trees to ensure fast read and writes.
\end{itemize}

\subsection{Research}

\begin{itemize}
\item
  \textbf{Research Assistant, University of Illinois}, \emph{Spring 2015
  - Present}

  Working with Prof.~Robin Kravets in the field of Mobile Computing.
  Focused on development of Internet of Things. Developed an eco system
  of smart objects with Android, Estimote Eddystone Beacons and nRF51
  DK. Designed tests to analyze the scanning and advertising performance
  of Bluegiga BLED 112. Wrote an Android application to control sensors
  on nRF51 DK using Bluetooth Low Energy.
\end{itemize}

\subsection{Project Experience}

\begin{itemize}
\item
  \textbf{Rarity Operating System}, \emph{Fall 2014}

  Operating System with scheduler, file system and support for multiple
  applications. Worked in a team of four. Wrote file system drivers.
  Implemented paging support as well as system calls.
\item
  \textbf{CS Faculty Analysis}, \emph{Summer 2014}

  Scraped UIUC CS faculty data from cs.illinois.edu using Python.
  Analyzed the relation between research focus and department using R.
\item
  \textbf{Call Notes}, \emph{Spring 2014}

  Application to record, transcribe, parse user voice mail and send user
  the key points using SMS. Implemented in Ruby. Wrote the script using
  Twilio API.
\item
  \textbf{Driver Interface, Illini Formula Electric}, \emph{Fall 2014}

  Part of team building a fully functional electric car. Leader of
  driver interface subsystem. Worked with the Chassis subsystem to
  design the dash board. Implemented speedometer using Hall Effect
  Sensors and Arduino.
\end{itemize}

\subsection{Skills}

\begin{itemize}
\item
  \textbf{Advanced}: C++ • x86
\item
  \textbf{Intermediate}: Python • R • Javascript • Data Mining • Android
\end{itemize}

\end{document}
